The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-23 dit-paper_ieee.tex

	\subsection{The DBF feasibility test}
		We recall the necessary and sufficient feasability condition on monoprocessor
		platforms based on the demand-bound function \cite{baruah1999generalized,
		baruah1990algorithms}.

@@

		The following necessary and sufficient condition of feasibility
		based on the DBF is given in \cite{baruah1999generalized}:
		\begin{theorem}
			\begin{equation*}
				\begin{array}{c}
					\tau \: \text{is feasible}  \iff
					\dbf{t_1, t_2} \leqslant t_2 - t_1 \; \forall t_1, t_2 \mid  0 \leq t_1 \leq t_2
				\end{array}
			\end{equation*}
		\end{theorem}
        Indeed, if there exists values of $t_1$ and $t_2$ such that $\dbf{t_1, t_2} > t_2 - t_1$, it means that more than $t_2 - t_1$ units of computation have to be done in $t_2 - t_1$ units of time. Therefore the system is not feasible.

@@

	We thus checked the existence condition on 10000 systems generated by:
	\begin{itemize}
		\item Generating utilization values with the \texttt{UUniFast} algorithm described in \cite{bini2005measuring}, with parameters:
		\begin{itemize}
			\item $U_{tot}$ (system utilization) chosen uniformly between 0.25 and 0.75
			\item $n$ (number of tasks) set to several values (see Fig.~\ref{fig:noFPDIT})
		\end{itemize}
		\item Choosing the $T_i$ uniformly between 5 and 20 (in order to have a manageable value of $H$), which also gives us the $C_i = \lfloor U_i \, T_i \rfloor$
		\item Choosing the $O_i$ with a normal distribution of mean $T_{min}$ and standard deviation $\frac{T_{max} - T_{min}}{2}$
		\item Choosing the $D_i$ uniformly in the interval $[T_i - CDF(T_i - C_i), T_i]$, where $CDF$ varies between 0 and 1 and is called the \emph{Constrained Deadline Factor}. It allows us to generate systems where the deadlines are closer to the period.
	\end{itemize}

>>>>

	\subsection{The DBF feasibility test}
		We recall the necessary and sufficient feasability condition on uniprocessor
		platforms based on the demand-bound function \cite{baruah1999generalized,
		baruah1990algorithms}.

@@

		The following necessary and sufficient condition of feasibility
		based on the DBF is given in \cite{baruah1999generalized}:
		\begin{theorem}
			\begin{equation*}
				\begin{array}{c}
					\tau \: \text{is feasible}  \iff
					\dbf{t_1, t_2} \leqslant t_2 - t_1 \; \forall t_1, t_2 \mid  0 \leq t_1 \leq t_2
				\end{array}
			\end{equation*}
		\end{theorem}
        It is easy to see that the condition is at least necessary, as if there exists values of $t_1$ and $t_2$ such that $\dbf{t_1, t_2} > t_2 - t_1$, it means that more than $t_2 - t_1$ units of computation have to be done in $t_2 - t_1$ units of time. Therefore the system would not be feasible.

@@

	We thus checked the existence condition on 10000 systems generated by:
	\begin{itemize}
		\item Generating utilization values with the \texttt{UUniFast} algorithm described in \cite{bini2005measuring}, with:
		\begin{itemize}
			\item System utilization chosen uniformly between 0.25 and 0.75
			\item The number of tasks set to several values (see Fig.~\ref{fig:noFPDIT})
		\end{itemize}
		\item Choosing the $T_i$ uniformly between 5 and 20 (in order to have a manageable value of $H$), which also gives us the $C_i = \lfloor U_i \, T_i \rfloor$
		\item Choosing the $O_i$ with a normal distribution of mean $T_{min}$ and standard deviation $\frac{T_{max} - T_{min}}{2}$
		\item Choosing the $D_i$ uniformly in the interval $[T_i - CDF(T_i - C_i), T_i]$, where $CDF$ varies between 0 and 1 and is called the \emph{Constrained Deadline Factor}. It allows us to generate systems where the deadlines are closer to the period.
	\end{itemize}
